Subglacial and subaerial fluvial sediment transport capacity respond differently to water discharge variations

### 2024-03-21 Delaneyetal2024.tex
small changes

Water discharge measurements at the sub-hour timescale remain unavailable in many catchments, further limiting the ability of subglacial  sediment transport models to capture certain events.
The model outputs' variability in subglacial channels approaches that of subaerial ones over $1-5$ days of water aggregation time (Figure~\ref{fig:multi_run}), possibly resulting in parity in sediment transport capacity variations between subaerial and subglacial channels over these periods.
However, generally steeper hydraulic gradients of glaciers may cause elevated sediment transport capacity in subglacial channels (Figure\,\ref{fig:model_outs}). 
Even so, water discharge forcings aggregated over periods longer than days may omit key sediment discharge characteristics, such as the timing of peaks in sediment transport capacity (Figure~\ref{fig:model_outs}).

>>>>

Water discharge measurements at the sub-hour timescale remain unavailable in many catchments, further limiting the ability of subglacial  sediment transport models to capture certain events.
The model outputs' variability in subglacial channels approaches that of subaerial ones over $1-5$ days of water aggregation time (Figure~\ref{fig:multi_run}), possibly resulting in parity in sediment transport capacity variations between subaerial and subglacial channels over these periods.
Note that although variability between the events could remain comparable, water discharge forcings aggregated over periods longer than days may omit key sediment discharge characteristics, such as the timing of peaks in sediment transport capacity (Figure~\ref{fig:model_outs}).
